---
title: "HW4 204"
author: "Edaysi Bucio"
date: "29 de mayo de 2018"
output:
  html_document:
    df_print: paged
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Download packages and data base
```{r}

library(tidyverse)
library(knitr)
library(rmarkdown)
library(dplyr)
library(knitr)
library(readr)
library(car)
library(stargazer)
library(devtools)
install_github("andrewheiss/reconPlots")

library(readr)
Data4 <- read_csv("~/UCSB Bren School/Sping quarter/ESM 204 Costello class/Cap and trade assigment/HW4Data.csv")

View(Data4)

```

################################################################################################
# Question 1. 
# **  Write down a plausible functional form for the marginal cost of abatement for sector A. Use # regression analysis to estimate the parameters of that function.  Repeating this for sectors B, # C, and D will give you a model of the marginal cost of abatement function for each sector. **

Answer: The plausible form for the MCA are describe below. In the table below, are described all the regression parameter for each sector.

Functional form/models
$$ MCA(A) = -8.644 + (0.577 * Q)$$
$$ MCA(B) = 9.318 + (0.199 * Q)$$
$$ MCA(C) = -11.655 + (0.784 * Q)$$

$$ MCA(D) = 9.688 + (0.260 * Q)$$

```{r Funcion}

#Marginal cost of abatement is a function of units abated and price per quantity abated

ModelMCA <- lm(MC_A ~ Abatement, data = Data4)
ModelMCB <- lm(MC_B ~ Abatement, data = Data4)
ModelMCC <- lm(MC_C ~ Abatement, data = Data4)
ModelMCD <- lm(MC_D ~ Abatement, data = Data4)

#Table for each model and coeficient's value

stargazer(ModelMCA, ModelMCB, ModelMCC, ModelMCD, type = "text", title="Mariginal Cost of Abatement Regression Results", align=TRUE, dep.var.labels=c("Sector A","Sector B", "Sector C", "Sector D"),  no.space=TRUE, ci=TRUE, ci.level=0.95)

```

**How well do your models fit the data for each sector?  You may need to experiment with different functional forms. Produce a plot of the estimated marginal abatement cost functions in all four sectors (this plot should go in your memo)**

Answer: A plot below allow to describes how each of the model fit the data by sector. Likewise, R^2 values are describe in the above table.

```{r Plot}

## Plot of the MCA for each sector

par(mfrow = c(2,2)) #I want to see my MCA plots by sector, all in one frame

plot(Data4$Abatement, Data4$MC_A, pch = 16, cex = 1.3, col = "green4", main = "MCA Carbon Emissions for Sector A", xlab = "Units of Carbon Emissions (tons)", ylab = "Marginal Cost of Abatement ($/ton)") +
  abline(ModelMCA)

plot(Data4$Abatement, Data4$MC_B, pch = 16, cex = 1.3, col = "green4", main = "MCA Carbon Emissions for Sector B", xlab = "Units of Carbon Emissions (tons)", ylab = "Marginal Cost of Abatement ($/ton)")  +
  abline(ModelMCB)

plot(Data4$Abatement, Data4$MC_C, pch = 16, cex = 1.3, col = "green4", main = "MCA Carbon Emissions for Sector C", xlab = "Units of Carbon Emissions (tons)", ylab = "Marginal Cost of Abatement ($/ton)")  +
  abline(ModelMCC)

plot(Data4$Abatement, Data4$MC_D, pch = 16, cex = 1.3, col = "green4", main = "MCA Carbon Emissions for Sector D", xlab = "Units of Carbon Emissions (tons)", ylab = "Marginal Cost of Abatement ($/ton)") +
  abline(ModelMCD)

```


########################################################################################################
# Question 2. 
# **Using these models and the current level of carbon emissions, derive each sector's demand curve for  # carbon emissions. In other words, how much would each sector be willing to pay for the right to pollute # the first unit, second unit, etc? Draw these demand curves on a graph. 

#Which sector is is willing to pay the most for the first unit of carbon emissions?

Answer: Sector C (put a name) is willing to pay the most for the first unit of carbon emissions = $160.825. Willigness to pay for units of carbon is shown in the graph below. 
#########################################################################################################

```{r Demand_curve}
#A = 180 #Current carbon emissions
#B = 200
#C = 220
#D = 300

# Create new columns of WTP values in the Data base with mutate function
Data4<-Data4%>% mutate (WTP_A = -8.644 + (0.577 * (180 - Abatement)))
Data4<-Data4%>% mutate (WTP_B = 9.318 + (0.199 * (200 - Abatement)))
Data4<-Data4%>% mutate (WTP_C = -11.655 + (0.784 * (220 - Abatement)))
Data4<-Data4%>% mutate (WTP_D = 9.688 + (0.260 * (300 - Abatement)))
                        
View(Data4)

#Plot sectors WTP
ggplot(Data4, aes(x = Abatement)) + 
  geom_line(aes(y = WTP_A), colour="aquamarine4", size = 0.9) + 
  geom_line(aes(y = WTP_B), colour = "chocolate4", size = 0.9) + 
  geom_line(aes(y = WTP_C), colour = "coral3", size = 0.9) +
  geom_line(aes(y = WTP_D), colour = "orange3", size = 0.9) +
  ylab(label="Marginal Cost of Abatement ($/ton)") + 
  xlab("Units of Carbon Emissions (tons)") + 
  theme_classic() +
  ggtitle("Demand for Carbon Emissions by Sector")


```

$$ WTPA = -8.644 + 0.577 * (180 - Q) $$

##################################################################################################
# Q. 3 Now focus on country X (which contains sectors A, B, and C). Assume there are no "co-benefits" 
#from carbon abatement (i.e. that there are no local pollutants that are affected by carbon abatement). #Suppose to meet the Paris Accord commitments, country X needs to cut all carbon emissions in half. 

#a. Cap on carbon. Each sector (A, B, and C) must cut its carbon emissions by 100 tons (thus reducing #total emissions from 600 down to 300).
Answer: Forgone benefits, or costs for not being able to pollute as much as each sector is willing is of 4331.7 for sector A, $3916.8 for sector B, and 12162.5 for sector C. The total cost for country X (The US) is of 20,411.

```{r Cap}
### The US

# 1. Total cost of meeting the target in country X #$20,411

Cut_emissions <- (180-80) + (200-100) + (220 - 120)
print(Cut_emissions)
#300

#Cost of cut carbon emissions by 100 tons

MC_cutA = 37.516 #Value from DataBase Data4. 
MC_cutB =  29.218
MC_cutC = 82.425
  
#Finding the area under the demand curve that represent the cost to sectors

Totalsector_cost <- 4331.7 + 3916.8 + 12162.5 #Below are the equations per sector
print(Totalsector_cost)
#$20,411


#2. Cost (or benefit) to each sector
#Sector A
Cost_sectorA <- (MC_cutA*100)+(100*(49.118 - MC_cutA)/2)
print(Cost_sectorA)
#$4,331.7

#Sector B
Cost_sectorB <- (MC_cutB*100)+(100*(49.118 - MC_cutB)/2)
print(Cost_sectorB)
#$3,916.8

#Sector C
Cost_sectorC<- (MC_cutC*100)+(100*(160.825 - MC_cutC)/2)
print(Cost_sectorC)
#$12,162.5

```

#b. Tax on carbon. To emit a ton of carbon in country X, you must pay a tax of $t. You will need to find the tax that accomplishes the desired reduction. 

Answer: Country X needs to set a total tax of 11,992.76. One way to tackle this is that country X sets an equal tax for all the sectors. In conclusion, country X needs to set a tax of $39.975 to emit a ton of carbon. 

```{r Tax}

MC_100 <- c(37.516, 29.218, 82.425)
View(MC_100)

Ab_sectorA <- -0.58*(37.75) + 95.75
Ab_sectorB <- -0.199*(29.218) + 49.118
Ab_sectorC <- - 0.78 * (82.425) + 160.825

#Setting the tax
XA <- Ab_sectorA*37.516
XB <- Ab_sectorB*29.218
XC <- Ab_sectorC*82.425

Total_Xs <-sum(XA, XB, XC)
print(Total_Xs)
#Country X needs to set a tax of $11,992.76


```

#c. Cap and trade. Each sector (A, B, C) is allocated carbon permits equal to their current emissions minus 100 (same as in (a) above), thus achieving the total reduction of 300. Then, these three sectors are allowed to trade with each other. You will need to derive the outcome of that trading.

Answer:
Having the three sector polluting 300 tons of carbon emissions, sector B can purchase most of the permits = 51, this is because sector B is willing to pollut more than their actual emissions. On the other hand, sector A can sell 15 permits and sector C is willing to sell 41 permits. 

```{r Cap_Trade}

#Actual permits per sector. We are considering the cut of carbon emissions by 100 units for sector from the cap on carbon scenario. 
SA_permits <- 80
SB_permits <- 100
SC_permits <- 120

#Current emissions. Abatement per unit
CEA <- 95.216
CEB <- 49.118
CEC <- 160.825

#Number of permits to trade (sell, buy) per sector
Trading_SA <- 80 - 95.216 #-15.16   Round = - 15
Trading_SB <- 100 - 49.118 #50.882  Round = 51
Trading_SC <- 120 - 160.825 #-40.825 Round = -41

```

##################################################################################################################Part 4. Again, without any co-benefits, suppose that country Y (which only has one carbon-emitting sector, D) has no obligation to reduce its emissions. Country X asks country Y to enter the country X carbon market. Doing so would require country Y to put a cap on carbon emissions at its current level of emissions (300 tons), but would then allow country Y to sell carbon offsets to sectors A, B, or C.  

Are there any incentives for country Y to enter country X's carbon market and to thus place a voluntary cap on its emissions?  Are there any incentives for country X to try to attract country Y into its market?#######################################################

```{r}

#Jessica section

```

################################################################################################################### Part 5. Now assume that every ton of carbon emissions creates 1 ton of local air pollution. Local air pollution causes economic damages (health, environmental, etc.), but only in the country in which it is emitted. Assume there are no local air pollution regulations in either country X or country Y. 


#a. In a carbon cap and trade market that only covers sectors in country X, how much local air pollution would you expect in country X?  In country Y? 

Answer: Considering that in the cap and trade scenario are generated 300 tons of carbon emissions, and that 1 ton of carbon emissions creates 1 ton of local air pollution: We expect that regardless of the distribution of the rigth of pollution, there are going to exists 300 tons of local air pollution in country X. 


#b. If country Y enters the carbon market for country X (as in question 4 above), how much local pollution will there be in country X and country Y? 

Answer:Under this scenario, now country X can emmit more local pollution/carbon emissions, which are of 378.42 tones. Country Y can emmit under this scenario 222.64 tones of carbon emissions. Conclusion: If country Y enters to the carbon market, country X is beneficied because nos can emit more tones of carbon. 

```{r}

#Aggregate marginal cost of abatement 

#Quantity emmited by sector, considering the price per permit ($29.80)

QE_SA <- (95.216 - 29.80) / 0.577
QE_SB <- (49.118 - 29.80) / 0.199
QE_SC <- (160.825 - 29.80) / 0.78
QE_SD <- (87.688 - 29.80) / 0.260


LPBYC <- matrix(c(113.37, 97.07, 167.98, 222.64))
LPBYC <- as.table(LPBYC)
LPBYC

Sum_SX <- sum(QE_SA, QE_SB, QE_SC)
print(Sum_SX)
#378.42

#LPBYC = Local Pollution By Country


```


#c. What advice can you give country X and country Y about the desirability of allowing international trade of carbon emissions credits? 

We advis to Country X and Y to don't ente into the nternational trade of carbon emissions because the costs that they are going to afford, are higher than the benefits. 

For example, due to the fact of the differet carbon emissions of each sector in country X, and ther variety in willigness to pay for each unit of pollution, as well of their MCA, it is difficult to enter in to the international carbon market and cut their emissions by X amount (100 units). 



